Component-based Software Development Framework \\for Embedded IoT Devices（仮）

### 2017-11-07 ipsj/paper.tex
Remove spaces of Fig.xx

This section describes the system model of the proposed framework, including basic technologies such as TECS.
The system model of the proposed framework is shown in Fig. \ref{fig:SystemModel}.

@@

Fig. \ref{fig:TECSFlow} shows the development flow using TECS.
TECS generator generates the interface code (.H and .C) and the configure file of the RTOS (.cfg) from the CDL file.

@@

TLSF algorithm classifies memory blocks into two stages and searches for a memory block that is optimal for the requested memory size.
The overview of TLSF algorithm is shown in Fig. \ref{fig:TLSF}.
Consider a case where a request, $malloc(100)$, is called to allocate a memory.
In the first step, it is classified by the most significant bit of the requested memory size.
In this case, since 100 is represented by binary number as 1100100, it is in the range from 64 to 128 from the most significant bit.
In the second step, it is further classified.
In this case, 64 to 128 are divided into 4, and 100 is in the block of 96 to 111.
Free block \footnote{Free block is an available memory block.} in this range is used.

@@

Fig. \ref{src:TLSFSignature} is a signature description for memory management used by the allocator.
It defines the memory pool initialization function {\it initializeMemoryPool}, memory allocation function {\it calloc}, {\it malloc}, {\it realloc}, and memory release function {\it free} as a signatures.

@@

The celltype description of the TLSF memory allocator component is shown in Fig. \ref{src:TLSFCelltype}.
An entry port, {\it eMalloc}, is connected to all components that perform memory management such as $malloc$ and $free$.
Here, {\it [inline]} is a specifier for Implementation as inline functions.
A memory pool size is defined as an attribute, and a pointer to a memory pool is defined as an variable.
Each component holds its own heap area, so even when calling functions for memory management at the same time in different threads, it is possible to operate without memory contention.

@@

As shown in Fig. \ref{fig:WithoutTECS}, since TLSF before componentization shares the heap area with multiple threads, if memory is allocated or released simultaneously from multiple threads, memory competition may occur in some cases.
In the research, TLSF is componentized using TECS as shown in Fig. \ref{fig:WithTECS}.
It is possible to operate in thread safe without exclusive control, because each component independently holds a heap area and manages memory within it.

@@

Fig. \ref{src:TLSFBuild} shows the build description of the TLSF memory allocator component shown in Fig. \ref{fig:WithTECS}\footnote{Other call/entry ports, attributes, and valuables are actually described, but it is omitted here for the simplicity.}.
Two sets of task components and TLSF components are combined.
Each memory pool size can be configured as an variable (Lines 5 and 11 in Fig. \ref{src:TLSFBuild}).
Fig. \ref{src:TLSFC} is the part of the code actually calling the function of the TLSF memory allocator component.
The use part shows a function that the mruby VM allocates memory in the mruby on TECS framework\cite{par:mrubyonTECS}\cite{par:mrubyonTECS2} which is introduced in Section \ref{sec:mrubyonTECS}.
Lines 8 calls the {\it free} function of the TLSF memory allocator component.
{\it cMalloc\_} represents the name of the calle port (Lines 2 in Fig. \ref{src:TLSFBuild}).
Likewise, Lines 13 and 17 call the function for memory allocation.
The heap area of {\it TLSFMalloc\_001} component is used if the code of \ref{src:TLSFC} is executed in {\it Task\_001}, and if that is executed in {\it Task\_002}, the heap area of {\it TLSFMalloc\_002} component is used, respectively.
In this way, in the component-based development using TECS, it is possible to operate with the same code without modifying the C code, although the cells are different.

>>>>

This section describes the system model of the proposed framework, including basic technologies such as TECS.
The system model of the proposed framework is shown in Fig.\ref{fig:SystemModel}.

@@

Fig.\ref{fig:TECSFlow} shows the development flow using TECS.
TECS generator generates the interface code (.H and .C) and the configure file of the RTOS (.cfg) from the CDL file.

@@

TLSF algorithm classifies memory blocks into two stages and searches for a memory block that is optimal for the requested memory size.
The overview of TLSF algorithm is shown in Fig.\ref{fig:TLSF}.
Consider a case where a request, $malloc(100)$, is called to allocate a memory.
In the first step, it is classified by the most significant bit of the requested memory size.
In this case, since 100 is represented by binary number as 1100100, it is in the range from 64 to 128 from the most significant bit.
In the second step, it is further classified.
In this case, 64 to 128 are divided into 4, and 100 is in the block of 96 to 111.
Free block \footnote{Free block is an available memory block.} in this range is used.

@@

Fig.\ref{src:TLSFSignature} is a signature description for memory management used by the allocator.
It defines the memory pool initialization function {\it initializeMemoryPool}, memory allocation function {\it calloc}, {\it malloc}, {\it realloc}, and memory release function {\it free} as a signatures.

@@

The celltype description of the TLSF memory allocator component is shown in Fig.\ref{src:TLSFCelltype}.
An entry port, {\it eMalloc}, is connected to all components that perform memory management such as $malloc$ and $free$.
Here, {\it [inline]} is a specifier for Implementation as inline functions.
A memory pool size is defined as an attribute, and a pointer to a memory pool is defined as an variable.
Each component holds its own heap area, so even when calling functions for memory management at the same time in different threads, it is possible to operate without memory contention.

@@

As shown in Fig.\ref{fig:WithoutTECS}, since TLSF before componentization shares the heap area with multiple threads, if memory is allocated or released simultaneously from multiple threads, memory competition may occur in some cases.
In the research, TLSF is componentized using TECS as shown in Fig.\ref{fig:WithTECS}.
It is possible to operate in thread safe without exclusive control, because each component independently holds a heap area and manages memory within it.

@@

Fig.\ref{src:TLSFBuild} shows the build description of the TLSF memory allocator component shown in Fig.\ref{fig:WithTECS}\footnote{Other call/entry ports, attributes, and valuables are actually described, but it is omitted here for the simplicity.}.
Two sets of task components and TLSF components are combined.
Each memory pool size can be configured as an variable (Lines 5 and 11 in Fig.\ref{src:TLSFBuild}).
Fig.\ref{src:TLSFC} is the part of the code actually calling the function of the TLSF memory allocator component.
The use part shows a function that the mruby VM allocates memory in the mruby on TECS framework\cite{par:mrubyonTECS}\cite{par:mrubyonTECS2} which is introduced in Section \ref{sec:mrubyonTECS}.
Lines 8 calls the {\it free} function of the TLSF memory allocator component.
{\it cMalloc\_} represents the name of the calle port (Lines 2 in Fig.\ref{src:TLSFBuild}).
Likewise, Lines 13 and 17 call the function for memory allocation.
The heap area of {\it TLSFMalloc\_001} component is used if the code of \ref{src:TLSFC} is executed in {\it Task\_001}, and if that is executed in {\it Task\_002}, the heap area of {\it TLSFMalloc\_002} component is used, respectively.
In this way, in the component-based development using TECS, it is possible to operate with the same code without modifying the C code, although the cells are different.
